Python as a machine learning language: experiences from the scikit-learn project

### 2013-05-01 paper.tex
Typo
counted number of contributors
explain double underscore syntax on pipelines

The scikit-learn project started in 2009 and has since been developed
by a team largely consisting of scientists
(both from computer science and other fields).
Its popularity can be gauged from various sources:
% TODO: list volume on the mailing list, number of contributors,
% number of issues opened and closed, number of surveys filled in.
at the time of writing,
the popular programmer's Q~\&{}A site StackOverflow\footnote{
  \url{http://stackoverflow.com/questions/tagged/scikit-learn}}
% update the following figure when paper is finalized
lists, at the time of writing, 322 scikit-learn-related questions.

@@

By composing, say, a \texttt{CountVectorizer} object
(which extracts term frequency features from text documents
according to a bag-words model),
a \textsf{tf--idf} transformer, a $\chi^2$ feature selector and a linear SVM,
one obtains a pipeline object with various hyperparameters:
whether to do stopword filtering,
linear vs.\ logarithmic \textsf{tf}, number of features to keep,
SVM regularization ($L_1$ or $L_2$ norm, strength $C$) a.o.
Such a composite \texttt{Pipeline} object
exposes all of these parameters using a special syntax;
each estimators must be given a name,
and if the SVM's name is, e.g., \texttt{linearsvm},
then its $C$ parameter is exposed as \texttt{linearsvm\_\_C}.

>>>>

The scikit-learn project started in 2009 and has since been developed
by a team largely consisting of scientists
(both from computer science and other fields).
Its popularity can be gauged from various sources:
% TODO: list volume on the mailing list, number of contributors,
% number of issues opened and closed, number of forks, number of surveys filled in.
at the time of writing,
the popular programmer's Q~\&{}A site StackOverflow\footnote{
  \url{http://stackoverflow.com/questions/tagged/scikit-learn}}
% update the following figure when paper is finalized
lists 322 scikit-learn-related questions.
At the time of writing,  % ddaa494c116e3c16bf032003c5cccbed851733d2
version control logs for the development version of scikit-learn
show 183 contributors to the project's source code and documentation
(after manual deduplication).

@@

By composing, say, a \texttt{CountVectorizer} object
(which extracts term frequency features from text documents
according to a bag-words model),
a \textsf{tf--idf} transformer, a $\chi^2$ feature selector and a linear SVM,
one obtains a pipeline object with various hyperparameters:
whether to do stopword filtering,
linear vs.\ logarithmic \textsf{tf}, number of features to keep,
SVM regularization ($L_1$ or $L_2$ norm, strength $C$) a.o.
Such a composite \texttt{Pipeline} object
exposes all of these parameters using a special syntax;
each estimators must be given a name,
and if the SVM's name is, e.g., \texttt{linearsvm},
then its $C$ parameter is exposed as \texttt{linearsvm\_\_C}.
The pipeline's \texttt{set\_params} splits the parameter names
on double underscores, uses the first part of the result
to look up the estimator,
and passes the second part to the estimator's own \texttt{set\_params}
as a keyword argument; due to Python's dynamic parameter passing,
the result is the same as if the user had called \texttt{set\_params}
on the SVM themselves.
(The double underscore syntax is not special to pipelines;
it is also employed in ensemble estimators such as random forests.)
